Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
small change to sec 8

There are cases where newly found controllers are due to the fact that the
optimiser can reason about infinite precision numbers and may therefore find
solutions that are not available using 64 bit plant precision (the maximum
allowed by the synthesiser in our implementation of standard CEGIS).

>>>>

There are cases where newly found controllers are due to the fact that the
optimiser can reason about infinite precision numbers and may therefore find
solutions that are not available using 64 bit plant precision, which
is the maximum allowed by the {\sc synthesize} phase in our implementation
(in standard CEGIS {\sc synthesize} is the only phase that can generate a
candidate controller).
